Labor Markets and Technological Change: Evidence from Electronic Health Records

### 2021-10-26 Presentations/ThirdYearPaperpres.tex
Updates from Overleaf

\begin{frame}{Event Studies}
\begin{equation*}
    Y_{it}=\alpha_t+\delta_i
\end{equation*}

@@

\begin{frame}{Intensive Margin}
\centering
\includegraphics[scale=.45]{Objects/event_plot.pdf}
\end{frame}

\begin{frame}{Intensive Margin}
\centering
\includegraphics[scale=.45]{Objects/event_hosp_plot.pdf}
\end{frame}

\begin{frame}{Hospital to Office?}
    \centering
    \includegraphics[scale=.5]{Objects/event_plot_office_to_hosp.pdf}
\end{frame}

\begin{frame}{Hospital to Office?}
    \centering
    \includegraphics[scale=.5]{Objects/event_hosp_plot_hosp_to_office.pdf}
\end{frame}

>>>>

\begin{frame}{Event Studies}

@@

\begin{frame}{Dep. Variable: Patients Billed with Hospitals}
\begin{figure}[ht]
        \begin{minipage}[b]{0.47\linewidth}
            \centering
            \includegraphics[width=\textwidth]{Objects/xtevent_fullsample.pdf}
            \caption{\small All Physicians\\}
        \end{minipage}
        \hspace{0.2cm}
        \begin{minipage}[b]{0.47\linewidth}
            \centering
            \includegraphics[width=\textwidth]{Objects/xtevent_oldsample.pdf}
            \caption{\small Phys. $>$ 35 yrs Experience}
        \end{minipage}
    \end{figure}
\end{frame}

\begin{frame}{Dep. Variable: Patients Billed with Hospitals}
\begin{figure}[ht]
        \begin{minipage}[b]{0.47\linewidth}
            \centering
            \includegraphics[width=\textwidth]{Objects/xtevent_hosp_fullsample.pdf}
            \caption{\small All Physicians \\(Only 1 Hospital)}
        \end{minipage}
        \hspace{0.2cm}
        \begin{minipage}[b]{0.47\linewidth}
            \centering
            \includegraphics[width=\textwidth]{Objects/xtevent_hosp_oldsample.pdf}
            \caption{\small Phys. $>$ 35yrs\\ (Only 1 Hospital)}
        \end{minipage}
    \end{figure}
\end{frame}

\begin{frame}{Dep. Variable: Probability of Billing, but not With Hospitals}
\begin{figure}[ht]
        \begin{minipage}[b]{0.47\linewidth}
            \centering
            \includegraphics[width=\textwidth]{Objects/xtevent_fullsample_ind.pdf}
            \caption{\small All Physicians}
        \end{minipage}
        \hspace{0.2cm}
        \begin{minipage}[b]{0.47\linewidth}
            \centering
            \includegraphics[width=\textwidth]{Objects/xtevent_oldsample_ind.pdf}
            \caption{\small Phys. $>$ 35yrs Experience}
        \end{minipage}
    \end{figure}
\end{frame}

\begin{frame}{Dep. Variable: Probability of Billing, but not With Hospitals}
\begin{figure}[ht]
        \begin{minipage}[b]{0.47\linewidth}
            \centering
            \includegraphics[width=\textwidth]{Objects/xtevent_hosp_fullsample_ind.pdf}
            \caption{\small All Physicians \\(Only 1 Hospital)}
        \end{minipage}
        \hspace{0.2cm}
        \begin{minipage}[b]{0.47\linewidth}
            \centering
            \includegraphics[width=\textwidth]{Objects/xtevent_hosp_oldsample_ind.pdf}
            \caption{\small Phys. $>$ 35yrs Experience\\ (Only 1 Hospital)}
        \end{minipage}
    \end{figure}
\end{frame}
